Title here

### 2016-12-06 portfolio/text/ms.Rmd
More copyediting

\caption{Individuals who fish permits and permit combinations (permit
strategies) with higher species diversity have lower expected revenue
variability. On the y-axis, dots, thick lines, and thin lines represent
posterior medians, 50\%, and 95\% credible intervals for the `r nstr` most
common permit strategies. Thick black line, and dark and light grey shaded
regions indicate median, 50\%, and 95\% credible intervals of strategy-level
regression built into the hierarchical model. Estimated variability represents
expected standard deviation for a permit holder who does not change species
diversity or days fished from year to year. }

@@

\caption{Effects of (A) generalizing and (B) specializing from year to year for
individual permit holders across the `r nstr` most common strategies. Changing
species diversity from year to year is associated with higher variability for
individuals within the strategies above the zero line. Generalizing (A) or
specializing (B) is associated with greater expected revenue to the right of the
zero line and lower expected revenue to the left of the zero line. These effects
are estimated holding fishing season length constant from year to year. Dots and
line segments represent medians and 50\% credible intervals of posteriors. }

>>>>

\caption{Individuals who fish permits and permit combinations (permit
strategies) with higher species diversity have lower expected revenue
variability. On the y-axis, dots, thick lines, and thin lines represent
posterior medians, 50\%, and 95\% credible intervals for the `r nstr` most
common permit strategies. Thick black line, and dark and light grey shaded
regions indicate median, 50\%, and 95\% credible intervals of strategy-level
regression built into the hierarchical model. Estimated variability represents
expected standard deviation for a permit holder who does not change species
diversity or days fished from year-to-year. }

@@

\caption{Effects of (A) generalizing and (B) specializing from year-to-year for
individual permit holders \emph{within} the `r nstr` most common strategies.
Changing species diversity from year-to-year is associated with higher
variability for individuals within the strategies above the zero line.
Generalizing (A) or specializing (B) is associated with greater expected revenue
to the right of the zero line and lower expected revenue to the left of the zero
line. These effects are estimated holding fishing season length constant from
year-to-year. Dots and line segments represent medians and 50\% credible
intervals of posteriors. }
